Turbulence in compact to giant H~II regions

### 2022-12-13 strucfunc_paper.tex
Finish the conclusions

\newcommand\vexp{\ensuremath{v_{\text{exp}}}}
An alternative interpretation,
as discussed in \citet{2011MNRAS.413..705L},
is that \(\sigma\los\) includes a contribution due to
ordered large-scale velocity gradients
(for instance, radial expansion)
in addition to the turbulence,
whereas \(\sigma\pos\) includes only the turbulent motions. 
% Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
Assuming a constant value \vexp{} for the ordered contribution
and that projection smoothing is negligible,
one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
which is shown by the dot-dashed line in Figure~\ref{fig:los-vs-pos}
for the case \(\vexp \approx \SI{8}{km.s^{-1}}\).
It can seen that such a relationship reproduces the 
observationally derived values equally as well as the linear fit.
On the other hand, we can rule out the possibility that
\vexp{} might increase in proportion to the turbulent velocity dispersion
since that would predict that \(\sigma\los \propto \sigma\pos\),
which is inconsistent with the observations as discussed above.

However, as pointed out by \citet{arthur2016turbulence},
the previous analysis is oversimplified since the presence
of density fluctuations (or, more generally, emissivity fluctuations)
means that the plane-of-sky dispersion of centroids \(\sigma\pos\)
is \emph{not} independent of the 
ordered large-scale velocity gradients along the line of sight.
Indeed, the neglect of any projection smoothing for the turbulent contribution
in the \citeauthor{2011MNRAS.413..705L} analysis is equivalent to
assuming \(\delta\kappa = -1\), which \emph{requires} substantial density fluctuations. 
This leads to a third potential explanation of the
\(\sigma\pos\)--\(\sigma\los\) relationship.
In the limit that the direct contribution of
turbulent velocity fluctuations is negligible
and that \(\sigma\los\) is entirely due to ordered expansion along the line of sight,
then a non-zero \(\sigma\pos\) can arise only from emissivity fluctuations,
which cause different parts of the ordered velocity field to be picked out
for different lines of sight.
A simple model of this process is explored in Appendix~\ref{sec:appar-veloc-fluct},
where a relation between the surface brightness dispersion and the apparent
velocity dispersions is derived.
This is compared with the behavior of the ratio
\(\sigma\pos / \sigma\los\) for
our observed sample in panel~i of Figure~\ref{fig:brightness-pdfs},
in which the solid and dashed lines show results for different assumptions
about the effects of velocity gradients on \(\sigma\los\).
Although the model does qualitatively reproduce the increase
in \(\sigma\pos / \sigma\los\) with increasing \(\sigma_S\), the quantitative agreement
is poor, with the model substantially overestimating the magnitude of
plane-of-sky fluctuations as compared with the line-of-sight widths.
This is evidence that the combination of a velocity gradient with
emissivity fluctuations is insufficient on its own,
and there must therefore be an additional disordered velocity component
in order to explain our observations.

@@

Expressed in the customary form \(L \sim  \sigma^\alpha\), our result corresponds to
\(\alpha = 4.0 \pm 1.6\), which is smaller than the value of \(\alpha \approx 5\) that is typically found
for more luminous regions
\citep{Moiseev:2015a, 2020ApJ...888..113W}
but not significantly so, given the uncertainty.
Studies that rely on \(\sigma\los\) generally find that
\(\sigma\) becomes insensitive to luminosity below about \(L(\ha) = \SI{e40}{erg.s^{-1}}\),
reaching a constant value of \(\sigma = \SI{15}{km.s^{-1}}\) \citep{Moiseev:2015a, Yu:2019a}.
On the other hand,
by using \(\sigma\pos\) instead of \(\sigma\los\),
we succeed in extending the same power-law relation
down to \(L(\ha) = \SI{2e37}{erg.s^{-1}}\) and \(\sigma = \SI{3}{km.s^{-1}}\).
Given our analysis of the previous section, one possible explanation for this
is that \(\sigma\pos\) is a better measure of the disordered turbulent motions within
the \hii{} regions, whereas \(\sigma\los\) is also affected by large-scale ordered motions,
which are always at least as large as the ionized sound speed.

@@

%The observations point out to the existence of spatial correlation between velocities, that could be interpreted as turbulence. 
%Arguments against the existence of true, isotropic turbulence can be raised as, for example: i) the histograms of velocity are not always Gaussian, ii) only a fraction of the integrated emission lines of the \hii{} regions show true Gaussian profiles. 
%The asymmetry in the emission line indicates coherent mass flow motions, 
%and sometimes is considered incompatible with turbulence. However, turbulence is in fact 
%a mixture of coherent and chaotic flows. 
%Only at the regime of the so-called fully developed turbulence the non-linear phenomena dominate completely the movement and the chaotic flow prevail. 
%The problem here is that a straightforward test for any turbulent model is a big challenge, as we are in the presence of many entangled effects. 
%However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.

Our analysis was able to characterize the velocity fields of a sample of \hii{} regions by determining a set of parameters unique to each velocity field which are: the correlation length, the exponent of a power law that fits the results through a determined range and the true velocity dispersion.
To achieve this, a new functional form for the second-order structure function was proposed. 
This new functional considers observational constraints such as the seeing, noise and the size of the observational box, effects that had not been considered before and play an important part in the interpretation of the structure function.
Our proposed functional form is used as an objective function in a non-linear regression to accurately determine the set of parameters related to turbulence and to the observational constraints.

The observed structure functions calculated in our work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a more realistic approach to determine and to the understanding the structure function.

Our analysis can be easily be expanded to other \hii{} regions with the possibility of comparing the results between them since our method guarantees homogeneity, providing the possibility to develop a future catalog of \hii{} regions turbulent parameters in a concise way.
By calculating the structure function of \hii{} regions with different morphologies, ages, stellar content, and dynamics it would be possible to detect the presence and the importance of different sources of mechanical energy, since the structure function would be different from one object to the other as we show in the present investigation.

Our methods could also been use to investigate the velocity fields of other phases of the interstellar medium.
The study of turbulence between ionized regions and the molecular clouds that give them birth can be carried out with the aid of a correct methodology with the intention of advancing the understanding of the kinematic relationships between them.

>>>>

\newcommand\vexp{\ensuremath{v_{\text{exp}}}}
An alternative interpretation,
as discussed in \citet{2011MNRAS.413..705L},
is that \(\sigma\los\) includes a contribution due to
ordered large-scale velocity gradients
(for instance, radial expansion)
in addition to the turbulence,
whereas \(\sigma\pos\) includes only the turbulent motions. 
% Constant v_exp : sig_los = sqrt(sig_pos**2 + v_exp**2)
Assuming a constant value \vexp{} for the ordered contribution
and that projection smoothing is negligible,
one would predict \(\sigma\los = (\sigma\pos^2 + \vexp^2)^{1/2}\),
which is shown by the dot-dashed line in Figure~\ref{fig:los-vs-pos}
for the case \(\vexp \approx \SI{8}{km.s^{-1}}\).
It can seen that such a relationship reproduces the 
observationally derived values almost as well as the linear fit.
On the other hand, we can rule out the possibility that
\vexp{} might increase in proportion to the turbulent velocity dispersion
since that would predict that \(\sigma\los \propto \sigma\pos\),
which is inconsistent with the observations as discussed above.

However, as pointed out by \citet{arthur2016turbulence},
the previous analysis is oversimplified since the presence
of density fluctuations (or, more generally, emissivity fluctuations)
means that the plane-of-sky dispersion of centroids \(\sigma\pos\)
is not independent of the 
ordered large-scale velocity gradients along the line of sight.
Indeed, the neglect of any projection smoothing for the turbulent contribution
in the \citeauthor{2011MNRAS.413..705L} analysis is equivalent to
assuming \(\delta\kappa = -1\), which \emph{requires} substantial density fluctuations. 
This leads to a third potential explanation of the
\(\sigma\pos\)--\(\sigma\los\) relationship.
In the limit that the direct contribution of
turbulent velocity fluctuations is negligible
and that \(\sigma\los\) is entirely due to ordered expansion along the line of sight,
then a non-zero \(\sigma\pos\) can arise only from emissivity fluctuations,
which cause different parts of the ordered velocity field to be picked out
for different lines of sight.
A simple model of this process is explored in Appendix~\ref{sec:appar-veloc-fluct},
where a relation between the surface brightness dispersion and the apparent
velocity dispersions is derived.
This is compared with the behavior of the ratio
\(\sigma\pos / \sigma\los\) for
our observed sample in panel~i of Figure~\ref{fig:brightness-pdfs},
in which the solid and dashed lines show results for different assumptions
about the effects of velocity gradients on \(\sigma\los\).
Although the model does qualitatively reproduce the increase
in \(\sigma\pos / \sigma\los\) with increasing \(\sigma_S\), the quantitative agreement
is poor, with the model substantially overestimating the magnitude of
plane-of-sky fluctuations as compared with the line-of-sight widths.
This is evidence that the combination of a velocity gradient with
emissivity fluctuations is insufficient on its own,
and that we require an additional disordered velocity component
in order to explain our observations.

@@

Expressed in the customary form \(L \sim  \sigma^\alpha\), our result corresponds to
\(\alpha = 4.0 \pm 1.6\), which is smaller than the value of \(\alpha \approx 5\) that is typically found
for more luminous regions
\citep{Moiseev:2015a, 2020ApJ...888..113W}
but not significantly so, given the uncertainty.
Studies that rely on \(\sigma\los\) generally find that
\(\sigma\) becomes insensitive to luminosity below about \(L(\ha) = \SI{e40}{erg.s^{-1}}\),
reaching a constant value of \(\sigma = \SI{15}{km.s^{-1}}\) \citep{Moiseev:2015a, Yu:2019a}.
On the other hand,
by using \(\sigma\pos\) instead of \(\sigma\los\),
we succeed in extending the same power-law relation
down to \(L(\ha) = \SI{2e37}{erg.s^{-1}}\) and \(\sigma = \SI{3}{km.s^{-1}}\).
Given our analysis of the previous section, one possible explanation for this
is that \(\sigma\pos\) is a better measure of the disordered turbulent motions within
the \hii{} regions than \(\sigma\los\) since the latter
is contaminated by large-scale ordered motions,
which are always at least as large as the ionized sound speed.

@@

We have used the second-order structure function of velocity centroids
on the plane of the sky to carry out a systematic study of the turbulent kinematics
in a sample of 9 \hii{} regions spanning a wide range of luminosities and sizes.
Our principal findings are as follows:
\begin{enumerate}[1.]
\item The velocity fluctuations range from subsonic (Mach number \(\Mach \approx 0.5\))
  in the case of low-luminosity Galactic regions, such as the Orion Nebula,
  up to supersonic (\(\Mach \approx 2.5\)) in the case of giant extragalactic regions
  such as 30~Doradus in the Large Magellanic Cloud. 
\item The correlation length of the velocity fluctuations is always a small fraction
  (roughly 2\%) of the \hii{} region diameter, implying that turbulent energy
  is injected on scales smaller than about 10\% of the size of each region.
\item The power law slope of the structure function at scales smaller than
  the correlation length is \(m \approx 1 \pm 0.2\) for all regions,
  with no significant correlation with size, luminosity, or velocity amplitude.
  This can be explained as due to a fortuitous cancellation
  between, on the one hand, a steepening underlying velocity spectrum and,
  on the other hand, a reduced role for projection smoothing as the turbulent fluctuations
  pass from the subsonic to the supersonic regime. 
\item The non-thermal component of the emission line widths (\(\sigma\los\)) is found
  to be proportional to the amplitude of the plane-of-sky velocity centroid fluctuations
  (\(\sigma\pos\)) with a slope of unity, but an offset such that
  \(\sigma\los \approx \SI{10}{km.s^{-1}}\) when \(\sigma\pos = 0\).
  This can be explained if \(\sigma\los\) is affected by ordered velocity fields,
  such as radial expansion, which leave no imprint on \(\sigma\pos\),
  implying that \(\sigma\pos\) is a better diagnostic of turbulent fluctuations than
  \(\sigma\los\), even though it is more challenging to measure.
\item On scales larger than the correlation length, a variety of behaviors are seen.
  Some regions, such as Carina and Hubble~X show uncorrelated homogeneous fluctuations
  at the largest scales, whereas others, such as Orion and 30~Doradus show evidence
  for large-scale gradients in the amplitude of the velocity fluctuations
  with more vigorous turbulence in the core of the nebula than in the outskirts.
  In other regions, such as the Lagoon Nebula and NGC~346, there is evidence
  for quasi-periodic oscillations on scales similar to the size
  of the mapped region. 
\end{enumerate}

% Our analysis was able to characterize the velocity fields of a sample of \hii{} regions by determining a set of parameters unique to each velocity field which are: the correlation length, the exponent of a power law that fits the results through a determined range and the true velocity dispersion.
% To achieve this, a new functional form for the second-order structure function was proposed. 
% This new functional considers observational constraints such as the seeing, noise and the size of the observational box, effects that had not been considered before and play an important part in the interpretation of the structure function.
% Our proposed functional form is used as an objective function in a non-linear regression to accurately determine the set of parameters related to turbulence and to the observational constraints.

% The observed structure functions calculated in our work does not reveal the precise characteristic of turbulence, but the statistical results that it provides allow us to determine a distinction between correlated or random velocity fluctuations in the photoionized gas, in which the presence of correlations in the velocity field is a inherent property of turbulence.
% Although this work is not conclusive about the nature of photoionized gas turbulence and a precise description of the origin and implications of these turbulent motions is out of the scope of our investigation, we believe that the tools presented here (see section~\ref{sec:methods-apply}) guarantee a more realistic approach to determine and to the understanding the structure function.

% Our analysis can be easily be expanded to other \hii{} regions with the possibility of comparing the results between them since our method guarantees homogeneity, providing the possibility to develop a future catalog of \hii{} regions turbulent parameters in a concise way.
% By calculating the structure function of \hii{} regions with different morphologies, ages, stellar content, and dynamics it would be possible to detect the presence and the importance of different sources of mechanical energy, since the structure function would be different from one object to the other as we show in the present investigation.

% Our methods could also been use to investigate the velocity fields of other phases of the interstellar medium.
% The study of turbulence between ionized regions and the molecular clouds that give them birth can be carried out with the aid of a correct methodology with the intention of advancing the understanding of the kinematic relationships between them.
